---
output: html_document
---
# Peer Assessment 1
RF Berg

```{r init,echo=FALSE}
library(plyr)
library(lattice)
setwd("/Users/richardberg/r/class/rr")
data<-read.csv("activity.csv")
```
```{r first,echo=FALSE}
d1<-data[! is.na(data$steps),]
d2<-ddply(d1,.(date),summarize,sum=sum(steps))
```
## What is mean total number of steps taken per day?
```{r hist,echo=FALSE}
hist(d2$sum,xlab="Mean Steps per Day",main="Histogram of Mean Steps")
```

```{r computetime, echo=FALSE }
mn<-mean(d2$sum)
md<-median(d2$sum)
```
The mean is `r mn` and median `r md`.


## What is the average daily activity pattern?
```{r timeser,echo=FALSE}
plot.ts(d1$steps,type='l',ylab="Total Daily Steps",main="Time Series for Steps on a 5 Minute Period")
```
```{r maxstep,echo=FALSE}
i1<-ddply(d1,.(interval),summarize,mean=mean(steps))
ind<-which.max(i1$mean)
intv<-i1$mean[ind]
intval<-i1$interval[ind]
```
This time interval `r intval` has the highest mean value of `r intv`.

## Imputing missing values
```{r imput,echo=FALSE}
m1<-data[is.na(data$steps),]
badLen<-length(m1$steps)
```
The number rows of missing data is `r badLen`

```{r fillin,echo=FALSE}
goodData<-read.csv("activity.csv")
goodData[is.na(goodData)]<-0
gd2<-ddply(goodData,.(date),summarize,sum=sum(steps))
hist(gd2$sum,xlab="Total Steps per Day",main="Histogram of Total Steps")
```

This shows that by changing NA to 0 changes the histogram by showing higher numbers >5000


## Are there differences in activity patterns between weekdays and weekends?
``` {r wends,echo=FALSE}
wd<-weekdays(as.Date(data$date))
wd<-gsub("Sunday","weekend",wd)
wd<-gsub("Saturday","weekend",wd)
wd<-gsub("Friday","weekday",wd)
wd<-gsub("Thursday","weekday",wd)
wd<-gsub("Wednesday","weekday",wd)
wd<-gsub("Tuesday","weekday",wd)
wd<-gsub("Monday","weekday",wd)
goodData<-cbind(wd=wd,goodData)
gd3<-ddply(goodData,.(interval,wd),summarize,sum=sum(steps))
xyplot(sum~interval|wd,data=gd3,ylab="Mean Steps per Day")
```

There is less activity on the weekends vs weekdays